\documentclass[a4paper,12pt,english]{article}

%Encoding and language
\usepackage[utf8]{inputenc}
\usepackage[russian]{babel}  %Removed Russian language support

%Math packages
\usepackage{amsmath,amsfonts,amssymb}

%Graphics
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, calc}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}  %Added to suppress PGFPlots warning

%Page geometry
\usepackage{geometry}
\geometry{top=2cm, bottom=2cm, left=2.5cm, right=2.5cm}

%Hyperlinks
\usepackage{hyperref}

%Floating objects
\usepackage{float}

%Additional packages
\usepackage{venndiagram}

%Title settings
\title{Homework}
\author{Student: \textbf{Rostislav Lokhov}}
\date{\today}

\begin{document}

%Title page
\begin{titlepage}
    \centering
    \vspace*{1cm}

    \Huge
    \textbf{Homework}

    \vspace{0.5cm}
    \LARGE
    Course: \textbf{English}

    \vspace{1.5cm}

    \textbf{Student: Rostislav Lokhov}

    \vfill

    \Large
    ANO HE Central University\\
    \vspace{0.3cm}
    \today

\end{titlepage}


\subsection{Task A}
\begin{enumerate}
    \item f j o b m a p c n i g e i d k h
\end{enumerate}

\subsection{Task B}
\begin{enumerate}
    \item Can you tell me what changes they made to the anti-harassment policy?
    \item Do you have any idea why HR didn’t respond to the complaint immediately?
    \item Do you know if employees can report bullying anonymously?
    \item Can you tell me when you are available next week?
    \item I wonder if there is an anti-harassment policy at our company?
\end{enumerate}

\subsection{Task D}
Dear Mr. Brooks,

I hope you’re doing well. I’m writing because I have a few questions regarding our new anti-harassment policy. As an employee, I’m eager to understand how this policy will be put into practice across our company.

Would you be able to let me know if there’s a detailed handbook available for everyone? Additionally, I’d appreciate any information on upcoming training sessions that might help us get a better grasp of the new guidelines and procedures.

Thank you for your time, and I look forward to hearing from you soon.

Best regards,
Rlohaw
\end{document}